Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-12-14 ms.tex
updated the OTIS fringe search stuff

The thin layer of NIRCam's HgCdTe detector can result in an interference pattern.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
The sca
A periodogram shows a peak near 19 pixels period, however, it is not an overwhelming periodic signature.
\textcolor{red}{double check the scatter in spectrum to photon + read noise}
\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum}
}\label{fig:integratedOtisGrismSpec}
\end{figure}

>>>>

The thin layer of NIRCam's HgCdTe detector can result in an interference pattern much like thin film interference on bubbles.
We investigate whether this can manifest itself on the spectrum with the NIRCam grism.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{otis_spec_and_norm.pdf}
\includegraphics[width=.49\columnwidth]{otis_spec_periodogram.pdf}
\caption{The integrated spectrum from Figure \ref{fig:ampOffsetsOtisGrismSlope} shows high frequency noise much far in excess of the spectrum's photon and read noise.
The spectrum is normalized by dividing by a spline fit (bottom left plot) to search for fringing effects
A periodogram shows a peak near 15 pixels period, however, it is not an overwhelming periodic signature.
\textcolor{red}{double check the scatter in spectrum to photon + read noise}
\textcolor{red}{Things to try: 1) keep looking for a fringing in the spectrum. Look at CV3 data, which has a tighter PSF}
}\label{fig:integratedOtisGrismSpec}
\end{figure}
